General constraints on magic distillation protocols from statistical mechanics

### 2021-06-05 magic_paper.tex
Quick proof that Wigner negativity coincides with Renyi entropy negativity for some \alpha

\subsubsection{Extention to general relative majorization}

>>>>

The following is a nice thing to establish.
\begin{theorem} A state $\rho$ has Wigner negativity if and only if $H_\alpha (W_\rho (\x)) < 0$ for some $\alpha >1$.
\end{theorem}
Let's try to prove this.
\begin{proof} If $H_\alpha (W_\rho(\x) <0 $ then this implies that $\log \sum_{\x} W_\rho (\x)^\alpha > 1$, however it is known that $H_\alpha$ is always non-negative on probability distributions and therefore $W_\rho(\x)$ must be a strict quasi-distribution with negativity.

Conversely, suppose $\rho$ has negativity in its Wigner representation. This implies that $\sum_{\x} |W_\rho (\x)| >1$. We now consider $\sum_{\x} W_\rho (\x)^{a/b}$ for $a/b >1$ and $a$ even and $b$ odd. We have that
\begin{align}
\sum_{\x} W_\rho (\x)^{a/b} &= \sum_{\x} |W_\rho (\x)|^{a/b} \nonumber \\
&= \sum_{\x} |W_\rho (\x)|^{1+ \epsilon},
\end{align}
where $\epsilon = a/b - 1 >0$. By choosing $a$ and $b$ appropriately we can make $\epsilon$ arbitrarily close to $0$ and therefore there exists a sequence $\epsilon_n$ such that
\begin{equation}
\sum_{\x} |W_\rho (\x)|^{1+ \epsilon_n} \rightarrow \sum_{\x} |W_\rho (\x)| >1.
\end{equation}
Therefore, $H_\alpha (W_\rho (\x)) <0 $ at some point in the sequence, which completes the proof.
\end{proof}
Therefore Wigner negativity coincides with negativity in at least one Renyi entropy.
\ddd{[Looking at this limit it almost feels like the $\alpha \rightarrow 0$ limit is actually giving mana....modulo the technical problem of taking the limit without calculus. I will think more about this point.]}
\subsubsection{Extention to general relative majorization}
